---
title: "MTHM 501: Campus Recuitrment Dataset Analysis"
author: "Jingjie Zhao"
date: "2020-11-16"
output: 
  pdf_document:
      latex_engine: xelatex
---

### Install packages
```
library(RColorBrewer)
library(ggplot2)
library(plyr)
library(dbplyr)
library(dplyr)
library(ggpubr)
library(tidyr)
library(GGally)
library(plotly)
library(gstat)
library(lattice)
library(sp)
```

# Import data
```{r}
library("rmarkdown")
setwd("/Users/jingjiezhao/Downloads")
campus_re <- read.csv("campus_recruitment.csv")
head(campus_re)
str(campus_re)
```


```{r}
# Replace column names
my_column_name <- c("serial_number", "gender", "ten_sec_edu_per", "ten_board_of_edu",
                    "twelve_sec_edu_per", "twelve_board_of_edu", "specialize_sec_edu",
                    "degree_percent", "degree_type_field", "work_ex", "entrence_test_per",
                    "MBA_specialize", "MBA_per", "hiring_status", "salary")
colnames(campus_re) <- my_column_name
colnames(campus_re)
```


```{r}
# Backup
campus_re_backup <- campus_re
campus_re_backup2 <- campus_re
```


```{r}
# Missing values
summary(is.na(campus_re_backup))
```

There is only salary column has missing values.Salary has null values because the students who aren't placed will not have any monthly payment. We can replace the null values with 0.


```{r}
# Imputing Missing Values
campus_re_backup[is.na(campus_re_backup)] <- 0
summary(is.na(campus_re_backup)) 
campus_re_backup2[is.na(campus_re_backup2)] <- 0
summary(is.na(campus_re_backup2))
```

# Data Visualization
### Univariate Exploration
```{r}
# 1. GENDER
# Check how many levels in "gender"
levels(campus_re_backup$gender)
# Count the frequency of each level in "gender"
sum(data.frame(campus_re_backup$gender) == "F")
sum(data.frame(campus_re_backup$gender) == "M")
# Percentage of each level
female_per <- (sum(data.frame(campus_re_backup$gender) == "F") /
                 length(campus_re_backup$gender)) * 100
female_per 
male_per <- (sum(data.frame(campus_re_backup$gender) == "M") / 
               length(campus_re_backup$gender)) * 100
male_per

# 2. 10th secondary Board of education 
# Check how many levels in "ten_board_of_edu"
levels(campus_re_backup$ten_board_of_edu)
# Count the frequency of each level in "ten_board_of_edu"
sum(data.frame(campus_re_backup$ten_board_of_edu) == "Central")
sum(data.frame(campus_re_backup$ten_board_of_edu) == "Others")
# Percentage of each level
central_10_per <- (sum(data.frame(campus_re_backup$ten_board_of_edu) == "Central") /
                     length(campus_re_backup$ten_board_of_edu)) * 100
central_10_per 
others_10_per <- (sum(data.frame(campus_re_backup$ten_board_of_edu) == "Others") / 
                    length(campus_re_backup$ten_board_of_edu)) * 100
others_10_per 


# 3. 12th secondary Board of education
# Check how many levels in "twelve_board_of_edu"
levels(campus_re_backup$twelve_board_of_edu)
# Count the frequency of each level in "twelve_board_of_edu"
sum(data.frame(campus_re_backup$twelve_board_of_edu) == "Central")
sum(data.frame(campus_re_backup$twelve_board_of_edu) == "Others")
# Percentage of each level
central_12_per <- (sum(data.frame(campus_re_backup$twelve_board_of_edu) == "Central") / 
                     length(campus_re_backup$twelve_board_of_edu)) * 100
central_12_per 
others_12_per <- (sum(data.frame(campus_re_backup$twelve_board_of_edu) == "Others") / 
                    length(campus_re_backup$twelve_board_of_edu)) * 100
others_12_per 


# 4. Higher Secondary Education - Specialization
# Check how many levels in "specialize_sec_edu"
levels(campus_re_backup$specialize_sec_edu)
# Count the frequency of each level in "specilize_sec_edu"
sum(data.frame(campus_re_backup$specialize_sec_edu) == "Arts")
sum(data.frame(campus_re_backup$specialize_sec_edu) == "Commerce")
sum(data.frame(campus_re_backup$specialize_sec_edu) == "Science")
# Percentage of each level
arts_per <- (sum(data.frame(campus_re_backup$specialize_sec_edu) == "Arts") / 
               length(campus_re_backup$specialize_sec_edu)) * 100
arts_per 
commerce_per <- (sum(data.frame(campus_re_backup$specialize_sec_edu) == "Commerce") / 
                   length(campus_re_backup$specialize_sec_edu)) * 100
commerce_per 
science_per <- (sum(data.frame(campus_re_backup$specialize_sec_edu) == "Science") / 
                  length(campus_re_backup$specialize_sec_edu)) * 100
science_per 


# 5. Degree Type (Field)
# Check how many levels in "degree_type_field"
levels(campus_re_backup$degree_type_field)
# Count the frequency of each level in "degree_type(field)"
sum(data.frame(campus_re_backup$degree_type_field) == "Comm&Mgmt")
sum(data.frame(campus_re_backup$degree_type_field) == "Others")
sum(data.frame(campus_re_backup$degree_type_field) == "Sci&Tech")
# Percentage of each level
c_m_per <- (sum(data.frame(campus_re_backup$degree_type_field) == "Comm&Mgmt") / 
              length(campus_re_backup$degree_type_field)) * 100
c_m_per 
s_t_per <- (sum(data.frame(campus_re_backup$degree_type_field) == "Sci&Tech") / 
              length(campus_re_backup$degree_type_field)) * 100
s_t_per 
others_per <- (sum(data.frame(campus_re_backup$degree_type_field) == "Others") / 
                 length(campus_re_backup$degree_type_field)) * 100
others_per 


# 6. Work Experience
# Check how many levels in "work_ex"
levels(campus_re_backup$work_ex)
# Count the frequency of each level in "work_ex"
sum(data.frame(campus_re_backup$work_ex) == "No")
sum(data.frame(campus_re_backup$work_ex) == "Yes")
# Percentage of each level
have_workex_per <- (sum(data.frame(campus_re_backup$work_ex) == "Yes")/ 
                      length(campus_re_backup$work_ex)) * 100
have_workex_per 
no_workex_per <- (sum(data.frame(campus_re_backup$work_ex) == "No") / 
                    length(campus_re_backup$work_ex)) * 100
no_workex_per 


# 7. MBA Specialization
# Check how many levels in "MBA_specialize"
levels(campus_re_backup$MBA_specialize)
# Count the frequency of each level in "MBA_specialize"
sum(data.frame(campus_re_backup$MBA_specialize) == "Mkt&Fin")
sum(data.frame(campus_re_backup$MBA_specialize) == "Mkt&HR")
# Percentage of each level
MF_per <- (sum(data.frame(campus_re_backup$MBA_specialize) == "Mkt&Fin") / 
             length(campus_re_backup$MBA_specialize)) * 100
MF_per 
MH_per <- (sum(data.frame(campus_re_backup$MBA_specialize) == "Mkt&HR") / 
             length(campus_re_backup$MBA_specialize)) * 100
MH_per 


# 8. Hiring Status
# Check how many levels in "hiring_status"
levels(campus_re_backup$hiring_status)
# Count the frequency of each level in "hiring_status"
sum(data.frame(campus_re_backup$hiring_status) == "Not Placed")
sum(data.frame(campus_re_backup$hiring_status) == "Placed")
# Percentage of each level
placed_per <- (sum(data.frame(campus_re_backup$hiring_status) == "Placed") / 
                 length(campus_re_backup$hiring_status)) * 100
placed_per 
not_placed_per <- (sum(data.frame(campus_re_backup$hiring_status) == "Not Placed") / 
                     length(campus_re_backup$hiring_status)) * 100
not_placed_per 


# 9. 10th sec edu per
# using "campus_re_backup2"
# Sectioning the 10th education percentage into 3 groups
# Note:
# Group1: 0% - 60%
# Group2: 61% - 80%
# Group3: 81% - 100%
campus_re_backup2[campus_re_backup2['ten_sec_edu_per']<=60,'ten_group']= "Group3"
campus_re_backup2[(campus_re_backup2['ten_sec_edu_per']>60) &
                    (campus_re_backup2['ten_sec_edu_per']<81),'ten_group']= "Group2"
campus_re_backup2[(campus_re_backup2['ten_sec_edu_per']>80) &
                    (campus_re_backup2['ten_sec_edu_per']<101),'ten_group']= "Group1"
# Convert chr to factor
class(campus_re_backup2$ten_group)
campus_re_backup2$ten_group <- as.factor(campus_re_backup2$ten_group)
str(campus_re_backup2)
# Check how many levels in "ten_group"
levels(campus_re_backup2$ten_group)
# Count the frequency of each level in "ten_group"
sum(data.frame(campus_re_backup2$ten_group) == "Group1")
sum(data.frame(campus_re_backup2$ten_group) == "Group2")
sum(data.frame(campus_re_backup2$ten_group) == "Group3")
# Percentage of each level
g1_per <- (sum(data.frame(campus_re_backup2$ten_group) == "Group1") / 
                 length(campus_re_backup2$ten_group)) * 100
g1_per 
g2_per <- (sum(data.frame(campus_re_backup2$ten_group) == "Group2") / 
                     length(campus_re_backup2$ten_group)) * 100
g2_per 
g3_per <- (sum(data.frame(campus_re_backup2$ten_group) == "Group3") / 
             length(campus_re_backup2$ten_group)) * 100
g3_per 


# 10. 12th sec edu per
# using "campus_re_backup2"
# Sectioning the 12th education percentage into 3 groups
# Note:
# Group1: 0% - 60%
# Group2: 61% - 80%
# Group3: 81% - 100%
campus_re_backup2[campus_re_backup2['twelve_sec_edu_per']<=60,'twelve_group']= "Group3"
campus_re_backup2[(campus_re_backup2['twelve_sec_edu_per']>60) &
                    (campus_re_backup2['twelve_sec_edu_per']<81),'twelve_group']= "Group2"
campus_re_backup2[(campus_re_backup2['twelve_sec_edu_per']>80) &
                    (campus_re_backup2['twelve_sec_edu_per']<101),'twelve_group']= "Group1"
# Convert chr to factor
class(campus_re_backup2$twelve_group)
campus_re_backup2$twelve_group <- as.factor(campus_re_backup2$twelve_group)
str(campus_re_backup2)
# Check how many levels in "ten_group"
levels(campus_re_backup2$twelve_group)
# Count the frequency of each level in "ten_group"
sum(data.frame(campus_re_backup2$twelve_group) == "Group1")
sum(data.frame(campus_re_backup2$twelve_group) == "Group2")
sum(data.frame(campus_re_backup2$twelve_group) == "Group3")
# Percentage of each level
g1_12_per <- (sum(data.frame(campus_re_backup2$twelve_group) == "Group1") / 
             length(campus_re_backup2$twelve_group)) * 100
g1_12_per 
g2_12_per <- (sum(data.frame(campus_re_backup2$twelve_group) == "Group2") / 
             length(campus_re_backup2$twelve_group)) * 100
g2_12_per 
g3_12_per <- (sum(data.frame(campus_re_backup2$twelve_group) == "Group3") / 
             length(campus_re_backup2$twelve_group)) * 100
g3_12_per 


# 11. Entrence test percentage
# using "campus_re_backup2"
# Sectioning the 12th education percentage into 3 groups
# Note:
# Group1: 0% - 60%
# Group2: 61% - 80%
# Group3: 81% - 100%
campus_re_backup2[campus_re_backup2['entrence_test_per']<=60,'entrence']= "Group3"
campus_re_backup2[(campus_re_backup2['entrence_test_per']>60) &
                    (campus_re_backup2['entrence_test_per']<81),'entrence']= "Group2"
campus_re_backup2[(campus_re_backup2['entrence_test_per']>80) &
                    (campus_re_backup2['entrence_test_per']<101),'entrence']= "Group1"
# Convert chr to factor
class(campus_re_backup2$entrence)
campus_re_backup2$entrence <- as.factor(campus_re_backup2$entrence)
str(campus_re_backup2)
# Check how many levels in "ten_group"
levels(campus_re_backup2$entrence)
# Count the frequency of each level in "ten_group"
sum(data.frame(campus_re_backup2$entrence) == "Group1")
sum(data.frame(campus_re_backup2$entrence) == "Group2")
sum(data.frame(campus_re_backup2$entrence) == "Group3")
# Percentage of each level
entr_1_per <- (sum(data.frame(campus_re_backup2$entrence) == "Group1") / 
                length(campus_re_backup2$entrence)) * 100
entr_1_per 
entr_2_per <- (sum(data.frame(campus_re_backup2$entrence) == "Group2") / 
                length(campus_re_backup2$entrence)) * 100
entr_2_per 
entr_3_per <- (sum(data.frame(campus_re_backup2$entrence) == "Group3") / 
                length(campus_re_backup2$entrence)) * 100
entr_3_per 


# 12. salary
# using "campus_re_backup2"
# Sectioning the 12th education percentage into 8 groups
# Note:
# Group0: 0 - 199999
# Group1: 200000 - 299999
# Group2: 300000 - 399999
# Group3: 400000 - 499999
# Group4: 500000 - 599999
# Group5: 600000 - 699999
# Group6: 700000 - 799999
# Group7: 800000 - 899999
# Group8: 900000 - 999999
campus_re_backup2[campus_re_backup2['salary'] < 200000,'salary_group']= "G0"
campus_re_backup2[(campus_re_backup2['salary'] >= 200000) &
                    (campus_re_backup2['salary'] < 300000),'salary_group']= "G1"
campus_re_backup2[(campus_re_backup2['salary'] >= 300000) &
                    (campus_re_backup2['salary'] < 400000),'salary_group']= "G2"
campus_re_backup2[(campus_re_backup2['salary'] >= 400000) &
                    (campus_re_backup2['salary'] < 500000),'salary_group']= "G3"
campus_re_backup2[(campus_re_backup2['salary'] >= 500000) &
                    (campus_re_backup2['salary'] < 600000),'salary_group']= "G4"
campus_re_backup2[(campus_re_backup2['salary'] >= 600000) &
                    (campus_re_backup2['salary'] < 700000),'salary_group']= "G5"
campus_re_backup2[(campus_re_backup2['salary'] >= 700000) &
                    (campus_re_backup2['salary'] < 800000),'salary_group']= "G6"
campus_re_backup2[(campus_re_backup2['salary'] >= 800000) &
                    (campus_re_backup2['salary'] < 900000),'salary_group']= "G7"
campus_re_backup2[(campus_re_backup2['salary'] >= 900000) &
                    (campus_re_backup2['salary'] < 1000000),'salary_group']= "G8"
# Convert chr to factor
class(campus_re_backup2$salary_group)
campus_re_backup2$salary_group <- as.factor(campus_re_backup2$salary_group)
str(campus_re_backup2)
# Check how many levels in "ten_group"
levels(campus_re_backup2$salary_group)
# Count the frequency of each level in "ten_group"
sum(data.frame(campus_re_backup2$salary_group) == "G0")
sum(data.frame(campus_re_backup2$salary_group) == "G1")
sum(data.frame(campus_re_backup2$salary_group) == "G2")
sum(data.frame(campus_re_backup2$salary_group) == "G3")
sum(data.frame(campus_re_backup2$salary_group) == "G4")
sum(data.frame(campus_re_backup2$salary_group) == "G5")
sum(data.frame(campus_re_backup2$salary_group) == "G6")
sum(data.frame(campus_re_backup2$salary_group) == "G7")
sum(data.frame(campus_re_backup2$salary_group) == "G8")
# Percentage of each level
sala_0_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G0") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_0_per 
sala_1_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G1") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_1_per 
sala_2_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G2") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_2_per 
sala_3_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G3") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_3_per 
sala_4_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G4") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_4_per 
sala_5_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G5") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_5_per 
sala_6_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G6") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_6_per 
sala_7_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G7") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_7_per 
sala_8_per <- (sum(data.frame(campus_re_backup2$salary_group) == "G8") / 
                 length(campus_re_backup2$salary_group)) * 100
sala_8_per 
```

### Univariate Histogram
```
graph1 <- ggplot(data = campus_re_backup, aes(x = gender)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Gender") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Comparison of Males and Females \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))
  
graph2 <- ggplot(data = campus_re_backup, aes(x = ten_board_of_edu)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Groups") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("10th Grade Board of Education \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph3 <- ggplot(data = campus_re_backup, aes(x = twelve_board_of_edu)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Groups") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("12th Grade Board of Education \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph4 <- ggplot(data = campus_re_backup, aes(x = specialize_sec_edu)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Faculty") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Higher Secondary Education - Specialization \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph5 <- ggplot(data = campus_re_backup, aes(x = degree_type_field)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Degree") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Higher Secondary Education Degree Type \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph6 <- ggplot(data = campus_re_backup, aes(x = work_ex)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Work Experience") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Work Experiences \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph7 <- ggplot(data = campus_re_backup, aes(x = MBA_specialize)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "MBA Specialization") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("MBA Specialization \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph8 <- ggplot(data = campus_re_backup, aes(x = hiring_status)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Status") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Hiring Status \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph9 <- ggplot(data = campus_re_backup2, aes(x = ten_group)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Percentage Groups") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Grade 10 Percentage Groups \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph10 <- ggplot(data = campus_re_backup2, aes(x = twelve_group)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Percentage Groups") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Grade 12 Percentage Groups \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph11 <- ggplot(data = campus_re_backup2, aes(x = entrence)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Percentage Groups") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Entrence Test Percentage \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

graph12 <- ggplot(data = campus_re_backup2, aes(x = salary_group)) +
  geom_bar(fill = "lightblue") +
  labs(y="Count", x = "Salary Groups") +
  theme_bw() +
  theme(text = element_text(size=10)) +
  ggtitle("Salary Distribution \n") +
  theme(plot.title = element_text(size = 10, face = "bold"))

ggarrange(graph1, graph2, graph3, graph4, graph5, graph6, 
          graph7, graph8, graph9, graph10, graph11, graph12, ncol = 3, nrow = 4)
```

**Conclusions:**

- We have about 140 male (65%) and 75 female students (35%) in our sample.
- We have about 116 students (54%) from Central Board and 99 students (46%) from Other Board.
- We have about 84 students (39%) from Central Board and 131 students (61%) from Other Board.
- We have about 11 students (5%) from Arts, 113 students (53%) from Commerce and 91 students (42%) from Science.
- We have 145 students (67%) from Commerce&Management, 70 students (32%) from Science&Technology and others.
- We can see that more students have no work experience before graduation. 
- There is NOT much difference in the number of our students specializing between Mkt&Fin and Mkt&HR. In comparison, slightly more students specizlize in Mkt&Fin.
- Majority of students were eventually hired by the company
- Majority of grade 10 students belong to Group2: 61% - 80% 
- Approximately half of the students who belong to Group1 in grade 10 rose to Group2. The proportion of students whose grades belong to the third group (Group3) has not changed much.
- The results of the entrance examination show that there is little difference in the number of students in each group. In comparison, 44% of the students belong to the second group, which is slightly more compare to Group1 (28%) and Group3 (27%).
- Most companies limit the salary package for campus recruitment from 200,000 to 400,000. We can see that salary in this range account for 63% of the entire sample.But it does not rule out that the company will offer high wages. One student in the sample received a salary of up to 940,000.
```
```
### Bivariate Exploration
```
data("iris")
```
```
# Check data type
str(campus_re_backup)

1. Restrict the dataset (NUM only)
campus_re_backup_bivariate <- campus_re_backup[,
                                               c("ten_sec_edu_per",
                                                 "twelve_sec_edu_per",
                                                 "degree_percent",
                                                 "entrence_test_per",
                                                 "MBA_per",
                                                 "salary",
                                                 "hiring_status")]

# Plot Histogram
a1<- ggpairs(campus_re_backup_bivariate,
             lower = list(continous = "smooth"),
             diag = list(continous = "barDiag"), 
             axisLabels = "show")
a1
a2 <- ggscatmat(campus_re_backup_bivariate, 
                columns = c("ten_sec_edu_per",
                            "twelve_sec_edu_per",
                            "degree_percent",
                            "entrence_test_per",
                            "MBA_per",
                            "salary"), 
                color = "hiring_status")
a2

2. gender & hiring Status
# Bar plot
graph13 <- campus_re_backup %>% 
  group_by(gender, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph13 <- ggplot(graph13, aes(hiring_status, counting, fill = gender)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with Gender \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette="Paired")
# Hiring percentage
male_hire_per <- (100 /140) * 100
male_hire_per 
female_hire_per <- ((148 - 100) / 75) * 100
female_hire_per 


3. ten_sec_edu_per & hiring status
# Box Plot
graph14 <- campus_re_backup %>%
  ggplot(aes(y = ten_sec_edu_per, fill = ten_sec_edu_per)) +
  geom_boxplot(aes(fill = hiring_status)) +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with G10 Percentage \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired") 


4. twevle_sec_edu_per & hiring status
# Box Plot
graph15 <- campus_re_backup %>%
  ggplot(aes(y = twelve_sec_edu_per, fill = twelve_sec_edu_per)) +
  geom_boxplot(aes(fill = hiring_status)) +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with G12 Percentage \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired") 


5. ten_board_of_edu & hiring status
graph16 <- campus_re_backup %>% 
  group_by(ten_board_of_edu, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph16 <- ggplot(graph16, aes(hiring_status, counting, fill = ten_board_of_edu)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with BoE(G10) \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette="Paired")


6. twelve_board_of_edu & hring status
# Bar plot
graph17 <- campus_re_backup %>% 
  group_by(twelve_board_of_edu, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph17 <- ggplot(graph17, aes(hiring_status, counting, fill = twelve_board_of_edu)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with BoE(G12) \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette="Paired") 


7. twelve_board_of_edu $ twelve_sed_edu_per
graph18 <- campus_re_backup %>%
  ggplot(aes(y = twelve_sec_edu_per, fill = twelve_sec_edu_per)) +
  geom_boxplot(aes(fill = twelve_board_of_edu)) +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Grade Percentage with BoE \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired") 


8. specialize_sec_edu & hiring status
graph19 <- campus_re_backup %>% 
  group_by(specialize_sec_edu, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph19 <- ggplot(graph19, aes(hiring_status, counting, fill = specialize_sec_edu)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with G12 Specialization \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired")


9. degree percentage & hiring status
graph20 <- campus_re_backup %>%
  ggplot(aes(y = degree_percent, fill = degree_percent)) +
  geom_boxplot(aes(fill = hiring_status)) +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with Degree Percentage \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired") 


10. degree type field & hiring status
graph21 <- campus_re_backup %>% 
  group_by(degree_type_field, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph21 <- ggplot(graph21, aes(hiring_status, counting, fill = degree_type_field)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with Degree Type \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired")

11. work_ex & hiring status
graph22 <- campus_re_backup %>% 
  group_by(work_ex, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph22 <- ggplot(graph22, aes(hiring_status, counting, fill = work_ex)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with Work Experience \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired")


12. entrence_test_per & hiring status
graph23 <- campus_re_backup %>%
  ggplot(aes(y = entrence_test_per, fill = entrence_test_per)) +
  geom_boxplot(aes(fill = hiring_status)) +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with Entrence Test Persentage \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired") 


13. MBA specialize & hiring status
graph24 <- campus_re_backup %>% 
  group_by(MBA_specialize, hiring_status) %>% 
  tally() %>% 
  complete(hiring_status, fill = list(n = 0)) %>% 
  mutate(counting = n)

graph24 <- ggplot(graph24, aes(hiring_status, counting, fill = MBA_specialize)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x ="Status", y = "Count") +
  theme_bw() +
  theme(text = element_text(size = 10)) +
  ggtitle("Hiring Status with MBA Specialization \n") +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  scale_fill_brewer(palette = "Paired")

ggarrange(graph13, graph14, graph15,
          graph16, graph17, graph18,
          graph19, graph20, graph21,
          graph22, graph23, graph24, ncol = 3, nrow = 4)
```

### Multivariate Exploration
```
# G10 grade, G12 grade, degree percent & salary (3D)
# Point colors
marker <- list(color = ~salary, 
               colorscale = c('#FFE1A1', '#683531'), 
               showscale = TRUE)
# Create the plot
plot1 <- plot_ly(campus_re_backup, 
             x = ~ten_sec_edu_per, 
             y = ~twelve_sec_edu_per, 
             z = ~degree_percent, marker = marker) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'G10 Percentage'),
                      yaxis = list(title = 'G12 Percentage'),
                      zaxis = list(title = 'Degree Percent')),
         annotations = list(
           x = 1.15,
           y = 1.05,
           text = 'Salary \n',
           showarrow = FALSE
         ))
plot1
```

### Model Fitting 1
```
## WHY PLACED (lm)
# Trying to find "fitted model"
# model1
str(campus_re_backup)
campus_re_backup[campus_re_backup['hiring_status'] == "Placed",'hire'] = "1"
str(campus_re_backup)
# Convert chr to num
campus_re_backup$hire <- as.numeric(campus_re_backup$hire)
# Only keep "Placed" status
campus_re_backup <- campus_re_backup[complete.cases(campus_re_backup), ]
str(campus_re_backup)
# model1
model1 <- lm(hire ~ serial_number +
               gender +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               twelve_board_of_edu +
               specialize_sec_edu +
               degree_percent +
               degree_type_field +
               work_ex +
               entrence_test_per +
               MBA_specialize +
               MBA_per +
               salary, data = campus_re_backup)
summary(model1)
## significant:
# degree_type_field
# twelve_sec_edu_per
# intercept

# plot
plot(model1, which = c(1, 2))
# Remove "MBA_per" (p = 0.90023)


# model2
model2 <- lm(hire ~ serial_number +
               gender +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               twelve_board_of_edu +
               specialize_sec_edu +
               degree_percent +
               degree_type_field +
               work_ex +
               entrence_test_per +
               MBA_specialize +
               salary, data = campus_re_backup)
summary(model2)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# Remove "specialize_sec_edu" (p = 0.77851)


# model3
model3 <- lm(hire ~ serial_number +
               gender +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               twelve_board_of_edu +
               degree_percent +
               degree_type_field +
               work_ex +
               entrence_test_per +
               MBA_specialize +
               salary, data = campus_re_backup)
summary(model3)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# Remove "twelve_board_of_edu" (p = 0.911418)


# model4
model4 <- lm(hire ~ serial_number +
               gender +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               degree_percent +
               degree_type_field +
               work_ex +
               entrence_test_per +
               MBA_specialize +
               salary, data = campus_re_backup)
summary(model4)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# Remove "work_ex" (p = 0.730570)


# model5
model5 <- lm(hire ~ serial_number +
               gender +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               degree_percent +
               degree_type_field +
               entrence_test_per +
               MBA_specialize +
               salary, data = campus_re_backup)
summary(model5)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# Remove "gender" (p = 0.641972)


# model6
model6 <- lm(hire ~ serial_number +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               degree_percent +
               degree_type_field +
               entrence_test_per +
               MBA_specialize +
               salary, data = campus_re_backup)
summary(model6)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# degree_percent
# Remove "salary" (p = 0.669565)


# model7
model7 <- lm(hire ~ serial_number +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               degree_percent +
               degree_type_field +
               entrence_test_per +
               MBA_specialize, data = campus_re_backup)
summary(model7)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# degree_percent
# Remove "MBA_specialize" (p = 0.224075)


# model8
model8 <- lm(hire ~ serial_number +
               ten_sec_edu_per +
               ten_board_of_edu +
               twelve_sec_edu_per +
               degree_percent +
               degree_type_field +
               entrence_test_per, data = campus_re_backup)
summary(model8)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# degree_percent
# Remove "ten_sec_edu_per" (p = 0.224693)


# model9
model9 <- lm(hire ~ serial_number +
               ten_board_of_edu +
               twelve_sec_edu_per +
               degree_percent +
               degree_type_field +
               entrence_test_per, data = campus_re_backup)
summary(model9)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# degree_percent
# entrence_test_per
# Remove "serial_number" (p = 0.21963)


# model10
model10 <- lm(hire ~ ten_board_of_edu +
                twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                entrence_test_per, data = campus_re_backup)
summary(model10)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# degree_percent
# entrence_test_per
# Remove "ten_board_of_edu" (p = 0.081713)


# model11
model11 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                entrence_test_per, data = campus_re_backup)
summary(model11)
## Significant:
# degree_type_field
# twelve_sec_edu_per
# intercept
# degree_percent
# Remove "entrence_test_per" (p = 0.053881)


# model12
model12 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field, data = campus_re_backup)
summary(model12)
##### ALL SIGNIFICANT #####

######################## Try add it back ###################

# fit13 = fit12 + ten_board_of_edu
model13 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                ten_board_of_edu, data = campus_re_backup)
summary(model13)
## p = 0.13969 DROP (NO ten_board_of_edu)


# fit14 = fit12 + serial_number
model14 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                serial_number, data = campus_re_backup)
summary(model14)
## p = 0.15005 DROP (NO serial_number)


# fit15 = fit12 + ten_sec_edu_per
model15 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                ten_sec_edu_per, data = campus_re_backup)
summary(model15)
## p = 0.25463 DROP (NO ten_sec_edu_per)


# fit16 = fit12 + MBA_specialize
model16 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                MBA_specialize, data = campus_re_backup)
summary(model16)
## p = 0.11591 DROP (NO MBA_specialize)


# fit17 = fit12 + salary
model17 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                salary, data = campus_re_backup)
summary(model17)
## p = 0.36321 DROP (NO salary)


# fit18 = fit12 + gender 
model18 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                gender, data = campus_re_backup)
summary(model18)
## p = 0.98047 DROP (NO gender)


# fit19 = fit12 + work_ex
model19 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                work_ex, data = campus_re_backup)
summary(model19)
## p = 0.25554 DROP (NO work_ex)


# fit20 = fit12 + twelve_board_of_edu
model20 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                twelve_board_of_edu, data = campus_re_backup)
summary(model20)
## p = 0.33794 DROP (NO twelve_board_of_edu)


# fit21 = fit12 + specialize_sec_edu
model21 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                specialize_sec_edu, data = campus_re_backup)
summary(model21)
## p(Commerce) = 0.55925 DROP (NO specialize_sec_eduCommerce)
## p(Science) = 0.66068 DROP (NO specialize_sec_eduScience)


# fit22 = fit12 + MBA_per
model22 <- lm(hire ~ twelve_sec_edu_per +
                degree_percent +
                degree_type_field +
                MBA_per, data = campus_re_backup)
summary(model22)
## p = 0.38016 DROP (NO MBA_per)

#############################
######## FINAL MODEL ########
#############################
summary(model12)

# residual plot:
plot(model12, which = c(1, 2))
```

### Model Fitting 2
```
## SALARY (lm)
# Trying to find "fitted model"
# fit1
campus_fit1 <- lm(salary ~ serial_number +
                    gender +
                    ten_sec_edu_per +
                    ten_board_of_edu +
                    twelve_sec_edu_per +
                    twelve_board_of_edu +
                    specialize_sec_edu +
                    degree_percent +
                    degree_type_field +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status, data = campus_re_backup2)
summary(campus_fit1)
## significant:
# hiring_statusPlaced
# MBA_per
# degree_type_fieldSci&Tech
# Remove "twelve_sec_edu_per" (p = 0.9334)


# fit2
campus_fit2 <- lm(salary ~ serial_number +
                    gender +
                    ten_sec_edu_per +
                    ten_board_of_edu +
                    twelve_board_of_edu +
                    specialize_sec_edu +
                    degree_percent +
                    degree_type_field +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit2)
## significant:
# hiring_statusPlaced
# MBA_per
# degree_type_fieldSci&Tech
# Remove "ten_board_of_edu" (p = 0.8534)


# fit3
campus_fit3 <- lm(salary ~ serial_number +
                    gender +
                    ten_sec_edu_per +
                    twelve_board_of_edu +
                    specialize_sec_edu +
                    degree_percent +
                    degree_type_field +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit3)
## significant:
# hiring_statusPlaced
# MBA_per
# degree_type_fieldSci&Tech
# Remove "serial_number" (p = 0.8079)


# fit4
campus_fit4 <- lm(salary ~ gender +
                    ten_sec_edu_per +
                    twelve_board_of_edu +
                    specialize_sec_edu +
                    degree_percent +
                    degree_type_field +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit4)
## significant:
# hiring_statusPlaced
# MBA_per
# degree_type_fieldSci&Tech
# Remove "twelve_board_of_edu" (p = 0.5799)


# fit5
campus_fit5 <- lm(salary ~ gender +
                    ten_sec_edu_per +
                    specialize_sec_edu +
                    degree_percent +
                    degree_type_field +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit5)
## significant:
# hiring_statusPlaced
# MBA_per
# degree_type_fieldSci&Tech
# Remove "specialize_sec_edu" (p = 0.4361)


# fit6
campus_fit6 <- lm(salary ~ gender +
                    ten_sec_edu_per +
                    degree_percent +
                    degree_type_field +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit6)
## significant:
# hiring_statusPlaced
# MBA_per
# Remove "degree_type_field" (p = 0.8535)


# fit7
campus_fit7 <- lm(salary ~ gender +
                    ten_sec_edu_per +
                    degree_percent +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit7)
## significant:
# hiring_statusPlaced
# MBA_per
# gender
# Remove "ten_sec_edu_per" (p = 0.6641)


# fit8
campus_fit8 <- lm(salary ~ gender +
                    degree_percent +
                    work_ex +
                    entrence_test_per +
                    MBA_specialize +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit8)
## significant:
# hiring_statusPlaced
# MBA_per
# gender
# intercept
# Remove "MBA_specialize" (p = 0.3143)


# fit9
campus_fit9 <- lm(salary ~ gender +
                    degree_percent +
                    work_ex +
                    entrence_test_per +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit9)
## significant:
# hiring_statusPlaced
# MBA_per
# gender
# intercept
# Remove "degree_percent" (p = 0.2994)


# fit10
campus_fit10 <- lm(salary ~ gender +
                    work_ex +
                    entrence_test_per +
                    MBA_per +
                    hiring_status,
                  data = campus_re_backup2)
summary(campus_fit10)
## significant:
# hiring_statusPlaced
# MBA_per
# gender
# intercept
# Remove "work_ex" (p = 0.21086)


# fit11
campus_fit11 <- lm(salary ~ gender +
                     entrence_test_per +
                     MBA_per +
                     hiring_status,
                   data = campus_re_backup2)
summary(campus_fit11)
## significant:
# hiring_statusPlaced
# MBA_per
# gender
# intercept
#Remove "entrence_test_per" (p = 0.1369)


# fit12
campus_fit12 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status,
                   data = campus_re_backup2)
summary(campus_fit12)

######################## Try add it back ###################

# fit13 = fit12 + work_ex
campus_fit13 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     work_ex,
                   data = campus_re_backup2)
summary(campus_fit13)
## p = 0.22826 DROP (NO work_ex)


# fit14 = fit12 + degree_percent
campus_fit14 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     degree_percent,
                   data = campus_re_backup2)
summary(campus_fit14)
## p = 0.367 DROP (NO degree_percent)


# fit15 = fit12 + MBA_specialize
campus_fit15 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     MBA_specialize,
                   data = campus_re_backup2)
summary(campus_fit15)
## p = 0.19425 DROP (NO MBA_specialize)


# fit16 = fit12 + ten_sec_edu_per
campus_fit16 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     ten_sec_edu_per,
                   data = campus_re_backup2)
summary(campus_fit16)
## p = 0.62998 DROP (NO ten_sec_edu_per)


# fit17 = fit12 + degree_type_field
campus_fit17 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     degree_type_field,
                   data = campus_re_backup2)
summary(campus_fit17)
## p(Others) = 0.71860
## p(Sci&Tech) = 0.11596 DROP (NO degree_type_field)


# fit18 = fit12 + specialize_sec_edu
campus_fit18 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     specialize_sec_edu,
                   data = campus_re_backup2)
summary(campus_fit18)
## p(Commerce) = 0.48079
## p(Science) = 0.43263 DROP (NO specialize_sec_edu)


# fit19 = fit12 + twelve_board_of_edu
campus_fit19 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     twelve_board_of_edu,
                   data = campus_re_backup2)
summary(campus_fit19)
## p = 0.57598 DROP (NO twelve_board_of_edu)


# fit20 = fit12 + serial_number
campus_fit20 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     serial_number,
                   data = campus_re_backup2)
summary(campus_fit20)
## p = 0.63659 DROP (NO serial_number)


# fit21 = fit12 + ten_board_of_edu
campus_fit21 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     ten_board_of_edu,
                   data = campus_re_backup2)
summary(campus_fit21)
## p = 0.82053 DROP (NO ten_board_of_edu)


# fit22 = fit12 + twelve_sec_edu_per
campus_fit22 <- lm(salary ~ gender +
                     MBA_per +
                     hiring_status +
                     twelve_sec_edu_per,
                   data = campus_re_backup2)
summary(campus_fit22)
## p = 0.97686 DROP (NO twelve_sec_edu_per)


#############################
######## FINAL MODEL ########
#############################
summary(campus_fit12)
plot(campus_fit1, c(1, 2))
plot(campus_fit12, c(1, 2))
```


### Spatial Modelling
```
# Exploring Stationarity
# Based on model 12
# hire ~ twelve_sec_edu_per + degree_percent + degree_type_field
# NOW,
# A.
# hiring_status & degree_percent, GIVEN degree_type_field
coplot(hiring_status ~ degree_percent | degree_type_field,
             data = campus_re_backup)
# hiring_status & degree_type_field, GIVEN degree_percent
coplot(hiring_status ~ degree_type_field | degree_percent,
             data = campus_re_backup)

# B.
# hiring_status & twelve_sec_edu_per, GIVEN degree_type_field
coplot(hiring_status ~ twelve_sec_edu_per | degree_type_field,
             data = campus_re_backup)
# hiring_status & degree_type_field, GIVEN twelve_sec_edu_per
coplot(hiring_status ~ degree_type_field | twelve_sec_edu_per,
             data = campus_re_backup)

# C.
# hiring_status & twelve_sec_edu_per, GIVEN degree_percent
coplot(hiring_status ~ twelve_sec_edu_per | degree_percent,
             data = campus_re_backup)
# hiring_status & degree_percent, GIVEN twelve_sec_edu_per
coplot(hiring_status ~ degree_percent | twelve_sec_edu_per,
             data = campus_re_backup)
```


###  Exploring Stationarity
```{r}
# Based on campus_fit12
# salary ~ gender + MBA_per + hiring_status
# NOW,
# A.
# salary & gender, GIVEN MBA_per
coplot(salary ~ gender | MBA_per,
       data = campus_re_backup)

# B.
# salary & MBA_per, GIVEN gender
coplot(salary ~ MBA_per | gender,
       data = campus_re_backup)
```


### Cumulative distribution function of salary 
```{r}
cdf_hiring_status <- ecdf(campus_re_backup$salary)
plot(cdf_hiring_status, verticals = T, do.points = F)
```




